Modeling thermal dust emission with the {\it PLANCK} 2015 release maps

### 2015-06-21 ms.tex
move Table 2 to appropriate section of the paper
starting to clean up the abstract and introduction

\shorttitle{\PLANCK~2015 Dust Modeling}

@@

\title{Modeling thermal dust emission in the {\it PLANCK} 2015 release maps}
\author{Aaron M. Meisner\altaffilmark{1,2}}
\author{Douglas P. Finkbeiner\altaffilmark{1,2}}
\altaffiltext{1}{Department of Physics, Harvard University, 17 Oxford Street, 
Cambridge, MA 02138, USA; ameisner@fas.harvard.edu}
\altaffiltext{2}{Harvard-Smithsonian Center for Astrophysics, 60 Garden St, 
Cambridge, MA 02138, USA; dfinkbeiner@cfa.harvard.edu}

@@

Based on the \PLANCK~2015 data release maps \citep{planck2015}, we present a 
thermal dust emission analysis analogous to that of \cite{meisner15}. We 
isolate thermal dust emission in the \PLANCK~2015 frequency maps, and present 
full-sky models of the unpolarized thermal dust emission using several 
paremeterizations of the dust spectrum, including single modified blackbody and
two-component models. The qualitative conclusions of \cite{meisner15} remain 
unchanged. In particular, the zodiacal light still represents the dominant 
systematic problem of our dust model on large angular scales, and the cosmic 
infrared background anisotropy remains the dominant systematic problem on small
angular scales.

@@

% iras first revolution in mapping ISM cirrus
While the dust in general lies within a disk a few hundred parsecs in scale 
height centered about the Galactic midplane, its detailed distribution is very 
patchy and cloudlike, as first revealed in far-infrared thermal emission by the
groundbreaking IRAS mission. Thus, it is of great importance to map 
interstellar dust over the entire sky, with high angular resolution and 
sensitivity.

% planck more recent breakthrough in mapping dust emission due to high
%     angular resolution / sensitivity of broad range of frequencies
The Planck mission (cite 2013 and 2015 release overview papers) has recently 
provided a breakthrough in full-sky mapping of emission from interstellar dust,
by obtaining relatively artifact free full-sky maps at XX frequencies from QQ 
to PP GHz, with a superb combination of near-IRAS resolution from QQ-PP and 
high sensitivity. Although these \PLANCK~maps contain various emission 
components, including the CMB, zodiacal light,and molecular emission, it is 
nevertheless possible to isolate exquisite maps of thermal emission from 
interstellar dust grains.
% mention the existing dust data products, say they're all very useful for
%     many purposes
Several full-sky data products currently exist for predicting emission and/or
extinction by interstellar dust. SFD - mention DIRBE temperature limitation.
Planck allows us to get around temperature limitation. One sentence overview of
Planck team's model. One or two sentences about Meisner+Finkbeiner modeling.

>>>>

\shorttitle{\PLANCK~2015 Thermal Dust}

@@

\title{Modeling thermal dust emission with the {\it PLANCK} 2015 release maps}
\author{Aaron M. Meisner\altaffilmark{1,2}}
\author{Douglas P. Finkbeiner\altaffilmark{1,2}}
\altaffiltext{1}{Department of Physics, Harvard University, 17 Oxford Street, 
Cambridge, MA 02138, USA; ameisner@fas.harvard.edu}
\altaffiltext{2}{Harvard-Smithsonian Center for Astrophysics, 60 Garden St, 
Cambridge, MA 02138, USA; dfinkbeiner@cfa.harvard.edu}

@@

Based on the \PLANCK~2015 data release maps \citep{planck2015}, we present a 
thermal dust emission analysis analogous to that of \cite{meisner15}. We 
isolate thermal dust emission in the \PLANCK~2015 frequency maps, and present 
full-sky models of the unpolarized thermal dust emission using several 
paremeterizations of the dust spectrum, including single modified blackbody and
two-component models. The qualitative conclusions of \cite{meisner15} remain 
unchanged. In particular, zodiacal light still represents the dominant 
systematic problem on large angular scales, and the cosmic infrared background 
anisotropy remains the dominant systematic problem on small angular scales.

@@

% iras first revolution in mapping ISM cirrus
While the dust generally lies within a disk a few hundred parsecs in scale 
height centered about the Galactic midplane, its detailed distribution is very 
patchy and cloudlike, as first revealed in far-infrared thermal emission by the
groundbreaking \IRAS~mission \citep{low84, wheelock94}. Thus, for the sake of 
studying cosmological foregrounds and the Galactic interstellar medium (ISM), 
it is of great importance to map the distribution of dust over the entire sky, 
with the best possible angular resolution and sensitivity.

% planck more recent breakthrough in mapping dust emission due to high
%     angular resolution / sensitivity of broad range of frequencies
The \PLANCK~mission \citep{planck2013,planck2015} has recently provided a 
breakthrough in full-sky mapping of emission from interstellar dust, by 
obtaining relatively artifact free, full-sky maps in nine bandpasses from QQ to
PP GHz, with a superb combination of near-IRAS resolution from QQ-PP and high 
sensitivity. Although these \PLANCK~maps contain various emission components, 
including the CMB, zodiacal light,and molecular emission, it is nevertheless 
possible to isolate exquisite maps of thermal emission from interstellar dust 
grains.
% mention the existing dust data products, say they're all very useful for
%     many purposes
Several full-sky data products currently exist for predicting emission and/or
extinction by interstellar dust. SFD - mention DIRBE temperature limitation.
Planck allows us to get around temperature limitation. One sentence overview of
Planck team's model. One or two sentences about Meisner+Finkbeiner modeling.
